\titleNameLong{}

### 2015-12-07 FinalProject/Tex/paper/paper.tex
fixed grammatical issue
reworded some of the abstract

\begin{abstract}
This article is a survey of the current state of general-purpose computing on
GPUs (GPGPUs) and the use of heterogeneous applications on them. The underlying
architecture of GPUs is well-suited to problems with a high level of data
parallelism and has traditionally been used for rendering computer graphics.
Performing general-purpose computing on GPUs is a relatively recent development,
having only become practical and popular in the past decade or so. A brief
overview of a typical GPU architecture is presented, and the challenges of
applying this architecture to heterogeneous problems is discussed. Several
different current areas of research are explored, including warp compression,
dynamic tuning of warps, managing contention between CPUs and GPUs, and compiler
management of heterogeneous applications. While the challenges presented are
difficult to overcome, general-purpose computing on GPUs continues to make
progress in the areas of performance, energy, and power.
\end{abstract}

>>>>

\begin{abstract}
This article is a survey of the current state of general-purpose computing on
GPUs (GPGPUs) and the use of heterogeneous applications on them. The underlying
architecture of GPUs is well-suited to problems with a high level of data
parallelism and has traditionally been used for rendering computer graphics.
Performing general-purpose computing on GPUs is a relatively recent development,
having only become practical and popular in the past decade or so. A brief
overview of a typical GPU architecture is presented, and the challenges of
applying this architecture to heterogeneous problems are discussed. Several
different current areas of research are explored, dynamic warp scheduling and
hardware tuning, reducing memory contention, and software solutions to the
challenges of GPGPU. While the challenges presented are difficult to overcome,
general-purpose computing on GPUs continues to make progress in the areas of
performance, energy, and power.
\end{abstract}
